%-------------------------
% Author : Jake Gutierrez
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage[T1]{fontenc} % higher quality font encoding
\usepackage[sfdefault]{universalis} % load the font and set it to default

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
     \textbf{#1} & \textbf{\small #2} \\
     \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

% New command for Technical Skills with Times New Roman
\newcommand{\resumeTechnicalSkills}[1]{
  {\fontfamily{ptm}\selectfont % Switch to Times New Roman
  \resumeItem{\textsl{Technical Skills: #1}}}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Sidney Lu (CHIA-HAO)} \\ \vspace{5pt}
    \LARGE{Full-Stack Algorithm Engineer, AI Agents} \\ \vspace{7pt}
    \small \raisebox{-0.1\height}\faGlobe\ \href{https://resume.posetmage.com}{\underline{resume.posetmage.com}} ~ 
    \href{mailto:mail@posetmage.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mail@posetmage.com}} ~     
    \href{https://github.com/HomunMage/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/HomunMage}}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart
    \resumeSubheading
      {Startup }{2023 - Present}
      {Full-Stack AI Agents Engineer, PM }{}
      \resumeItemListStart
        \resumeItem{Implemented AI-driven content systems with high scalability and fault tolerance using modern full-stack technologies on local PC with NVIDIA GPU. Document page: LangGraph-GUI: \underline{\href{https://langgraph-gui.github.io/}{(https://langgraph-gui.github.io/)}}}
        \resumeItem{Product management with a focus on achieving startup strategic direction, utilizing project management tools to drive efficient execution.}
        \resumeItem{Implemented LangGraph-ChatBot: Reduced inter-departmental communication and handover costs by implementing an AI chatbot system.}
        \resumeItem{Implemented Visual user Friendly frontend for CrewAI. CrewAI-GUI: \underline{\href{https://github.com/LangGraph-GUI/CrewAI-GUI}{ (https://github.com/LangGraph-GUI/CrewAI-GUI)}}}
        \resumeTechnicalSkills{ \\
        路 ai-end: Prompt Engineering, AI Agents, LLM, Ollama, LangChain, LangGraph, CrewAI \\
        路 frontend: Vue, React, JavaScript, Qt \\
        路 backend: RESTful API(Flask, FastAPI), Python \\
        路 infra: CI/CD, Docker Compose, Github-Action, Linux, Nginx, Shell Scripts}
      \resumeItemListEnd

    \resumeSubheading
    {Freelance Professional}{2023 - 2024}
    {Game Designer, PM, Algorithmic Trading}{}
        \resumeItemListStart
        \resumeItem{Designed game systems and mechanics. Improved game UI/UX experience.}
        \resumeItem{Planned game projects, managed schedules, and collaborated with customer client on game development timelines and budgets.}
        \resumeItem{Implemented algorithmic trading strategies in cryptocurrency, integrating traditional rule-based trading methodologies.}
        \resumeTechnicalSkills{Game Design, Project Management, Monday, Unity, C\#, TradingView, PineScript, Jekyll, JavaScript}
        \resumeItemListEnd

    \resumeSubheading
     {Qualcomm}{2022 - 2023}
     {Computer Vision R\&D / Systems and DSP Engineer}{}
     \resumeItemListStart
       \resumeItem{Developed approximation algorithms for 3D environment reconstruction, porting algorithms to mobile DSP chip, improving real-time performance.}
       \resumeItem{Worked with cross-functional teams to streamline integration with mobile chip architecture, optimizing system modulized.}
       \resumeTechnicalSkills{Computer Vision, Optimization, SIMD, C++, Python, DSP, CI / CD, Jenkins, Docker}
     \resumeItemListEnd

    \resumeSubheading
     {HTC ViveVR}{2018 - 2021}
     {R\&D Software Engineer / Graphics}{}
     \resumeItemListStart
       \resumeItem{Implemented and optimized VR algorithms for real-time rendering using DX12, ensuring high-performance, scalable solutions.}
       \resumeItem{Collaborated with hardware teams to integrate GPU optimization strategies and boost system performance for VR experiences.}
       \resumeItem{Optimized SDK with GPU profiling and benchmark tools such as GPUView, using Nvidia, AMD GPU hardware SDKs to speed up VR algorithms}
       \resumeTechnicalSkills{VR, Computer Graphics, Optimization, SIMD, GPGPU, DX11, DX12, HLSL, C++, Visual Studio}
     \resumeItemListEnd

     \resumeSubheading
     {samtsai.org/thecppnews/, C++ Newsletter}{2018 - 2021}
     {Contributing Writer, Authored technical articles about modern C++ }{}

     \resumeSubheading
     {HTC (Intern)}{2017}
     {Software Engineer Intern}{}
     \resumeItemListStart
       \resumeItem{Developed features for VR projects in close collaboration with cross-functional teams, gaining hands-on experience in scalable software solutions.}
       \resumeTechnicalSkills{Computer Vision, Machine Learning, Python}
     \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
     {National Chiao Tung University}{2016 - 2018}
     {Master of Science in Computer Science, Institute of Multimedia Engineering}{}

    \resumeSubheading
     {National Cheng Kung University}{2010 - 2014}
     {Bachelor of Science in Earth Sciences}{}

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
%\section{TECHNICAL SKILLS}

\end{document}
